Introduction

### 2025-01-22 choose_license.qmd

>>>>

::: {#nte-situation-lmu .callout-note collapse="true"}
### For researchers at LMU

If you are an employee at LMU and your funder does not mandate the use of a particular license, the decision of which license to use lies with the holder of your chair (_Lehrstuhlinhaber\*in_). The only exception is the case that you developed an invention you would like to exploit commercially with a patent. Then, you are required to officially report your invention to the IP management team of the LMU, which will work out the next steps with you.
:::

### 2025-01-22 index.qmd

Quarto is a tool to create reproducible documents, but not the only one. You may also use [RMarkdown](https://rmarkdown.rstudio.com/), [Jupyter Book](https://jupyterbook.org/), [Stencila](https://stencila.io/), [Curvenote](https://curvenote.dev/), [showyourwork!](https://show-your.work/), or one of the countless others.
:::

>>>>

Quarto is a tool to render dynamic documents, but not the only one. You may also use [`rmarkdown`](https://rmarkdown.rstudio.com/), [Jupyter Book](https://jupyterbook.org/), [Stencila](https://stencila.io/), [Curvenote](https://curvenote.dev/), [showyourwork!](https://show-your.work/), [Org Mode](https://orgmode.org/), [StatTag](https://sites.northwestern.edu/stattag/), or one of the countless others.
:::

### 2025-01-22 intro.qmd
Provide exact page reference

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take months to come up with a working solution, if possible at all. This situation has been put aptly by @Buckheit1995, distilling an idea by geophysicist Jon Claerbout:

> "An article about computational science in a scientific publication is not the scholarship itself, it is merely advertising of the scholarship. The actual scholarship is the complete software development environment and the complete set of instructions which generated the figures."

>>>>

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take months to come up with a working solution, if possible at all. This situation has been put aptly by Buckheit & Donoho [-@Buckheit1995, p. 59], distilling an idea by the geophysicist Jon Claerbout:

> "An article about computational science in a scientific publication is __not__ the scholarship itself, it is merely __advertising__ of the scholarship. The actual scholarship is the complete software development environment and the complete set of instructions which generated the figures."
